---
title: "Data607 Project 2C"
author: "Deepa"
date: "3/13/2022"
output: html_document
---



## For this assignment, I will be using the dataset from kaggle for superhero TV shows

Original link;https://www.kaggle.com/anoopkumarraut/superhero-tv-shows/data



#### Import Library

```{r}

library(tidyverse)
library(stringr)
library(tidyr)

```


#### Load data from Github (csv) into R dataframe

```{r}
df<- read.csv("https://raw.githubusercontent.com/deepasharma06/Data-607/main/Dataset_Superhero-TV-Shows.csv")
head(df)
```

### I will be focusing on two packages Tidyr and strigr

## Using tidyr package to clean the data

### using df function to remove the column

```{r}
library(tidyr)
df<- df[, c("show_title", "imdb_rating", "release_year", "genre")]
head(df)
```


#### The following code truncates the first 4 characters of release_year to get the year instead of a range.

#### It uses the substr function in stringr package. 
```{r}
df$release_year <- substr(df$release_year,1,4)
head(df)
```


#### This code is to replace any rows in imdb_rating column with a value of 'Not_Rated' with NA

```{r}
df$imdb_rating[df$imdb_rating == 'Not-Rated'] = NA
head(df)
```

#### This code is to replace any rows in imdb_rating column with a value of Null with NA

```{r}
df$imdb_rating[df$imdb_rating == ''] = NA
head(df)
```

#### This code is to replace any rows in release_year column with a value of 'TBA' with NA

```{r}
df$release_year[df$release_year == 'TBA'] = NA
head(df)
```

#### This code is to replace all rows with NA
### Using drop_na function from tidyr package

```{r}
df <- drop_na(df) 
head(df)
```




















